Age-related changes in plant growth and traits

### 2016-06-01 scripts/Accessory_figs_20160218.Rmd
figuring out why early dispersal costs are underestimated

>>>>

check <- subset(SummarySpp[["mean"]],species=="HEPU")
check$seed_size
check$embryo_endo_size
check$seed_costs
check$prepollen_costs
check$pack_disp_costs
check$pack_disp_costs_plus
check$pack_disp_early_costs
check$seed_early_costs

parts <- subset(PartsSummary,species=="HEPU")
parts

invest <- subset(InvestmentByPart,species=="HEPU"&part=="flower_calyx")
